A ``Dream'' Interface Design

### 2014-11-24 dream-design/dream-design.tex
system overview

@@

Even with these alternate forms of feedback, the literature suggests that insufficient feedback is still a major usability issue with touchscreen mobile devices. \cite{Tinwala:2010:ETE:18	68914.1868972, Kane:2011:UGB:1978942.1979001, Hardy:2008:TIT:1409240.1409267, El-Glaly:2013:TTF:2460625.2460665, Buxton:1986:HID:22339.22386}. A study by Hussain Tinwala and Scott MacKenzie submits that the lack of physical keys requires heightened visual attention from the user, which diverts the user's concentration from the thoughts being expressed \cite{Tinwala:2010:ETE:18 68914.1868972}. The lack of physical keys not only diverts the attention of some users, but it also makes the device  almost entirely unusable for others. A study from Virginia Polytechnic Institute and State University demonstrates how touchscreen mobile devices do not provide sufficient feedback for Individuals with Blindness or Severe Visual Impairment (IBSVI) as the users are only able to ``develop a spatial mental model for the interface or the screen through dead reckoning'' \cite{El-Glaly:2013:TTF:2460625.2460665}.

I have designed a ``dream'' interface for touchscreen mobile devices that aims to tackle some of these usability issues. My design provides a significant amount of tactile feedback that will be helpful for individuals without visual impairments and IBSVI alike.

\section{Top-Level Design}
\label{background}

>>>>

\section{Introduction}
\label{Introduction}

@@

Even with these alternate forms of feedback, the literature suggests that insufficient feedback is still a major usability issue with touchscreen mobile devices. \cite{Tinwala:2010:ETE:18	68914.1868972, Kane:2011:UGB:1978942.1979001, Hardy:2008:TIT:1409240.1409267, El-Glaly:2013:TTF:2460625.2460665, Buxton:1986:HID:22339.22386}. A study by Hussain Tinwala and Scott MacKenzie submits that the lack of physical keys requires heightened visual attention from the user, which diverts the user's concentration from the thoughts being expressed \cite{Tinwala:2010:ETE:18 68914.1868972}. The lack of physical keys not only diverts the attention of some users, but it also makes the device  almost entirely unusable for other users. A study from Virginia Polytechnic Institute and State University demonstrates how touchscreen mobile devices do not provide sufficient feedback for Individuals with Blindness or Severe Visual Impairment (IBSVI) as these users are only able to ``develop a spatial mental model for the interface or the screen through dead reckoning'' \cite{El-Glaly:2013:TTF:2460625.2460665}.

Thus, the aim of this investigation is to propose a ``dream'' interface design that addresses some of these usability issues.

In this investigation, I propose a ``dream'' interface design for touchscreen mobile devices that provides a significant amount of tactile feedback. This feedback is designed in a way that can be helpful for individuals with and without visual impairments alike. This design was developed with the usability metrics of learnability, efficiency, and errors in mind.

This design makes use of technology that is currently being created by Tactus, a company in Fremont California \cite{Tactus}. Tactus brings real physical buttons that dynamically appear and disappear into a flat touch screen (see Figure~\ref{tactus}). Small fluid channels are routed throughout the Tactile Layer and enable fluid ot expand the top polymer layer to create the physical buttons \cite{Tactus}.

Although this technology from Tactus is extremely bleeding-edge, it has already received a fair amount of recognition \cite{CNN, I-Zone, PCMag}.

\begin{figure}[ht]
\centering
\includegraphics[width=4.5in]{tactus1.jpg} 
\caption{Tactus Technology keyboard}
\label{tactus}
\end{figure}

\section{Top-Level Design}
The design aims to assist IBSVI engage their spatial cognition, perception and sensing resources while interacting with touch screens. The tactile stuff is intended to operate in conjunction with other technologies that provide auditory feedback that informs the users of \textit{what} is at the location on the screen while the tactile buttons heps the user know \textit{where} it is. 
\label{background}
